H2: Age Differences

### 2023-08-02 H1.Rmd
re-ran some analyses for paper (almost ready to submit)

@@

>>>>

test2 <- subset(test, p > .05)
test2

int_sig_pos <- test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
int_sig_neg <- test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
int_non_sig <- test2

@@

test2 <- subset(test, p > .05)
test2

symb_sig_pos <- test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
symb_sig_neg <- test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
symb_non_sig <- test2

### 2023-08-02 H1_semi_clean.Rmd
ran extra semi-clean analyses
re-ran some analyses for paper (almost ready to submit)

@@

@@

@@

>>>>

#### re-load ungrouped data ####
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
x$sex_01 <-  dplyr::recode(x$sex3,
               "male"="0"
              ,"female"="1")

@@

regression_fun <- function(x){
  fit <- lm(moral_identity_internal~sex_01+age, data = x)
  summary(fit)
}

all_regressions <- lapply(x, regression_fun)
all_regression_ps <- function(y){
  y$coefficients[11]
}
lapply(all_regressions, all_regression_ps)
regression_ps_for_table <- lapply(lapply(all_regressions, all_regression_ps), p_report)

@@

mean(df$moral_identity_internal,na.rm=T)
mean(df$moral_identity_symbolic,na.rm=T)

@@

test_with_regression <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, ps_for_table)
    ,do.call(rbind, regression_ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

test_with_regression <- `colnames<-`(test_with_regression, c("mean F","SD F","mean M", "SD M", "t","df","p","p2","d"))
test_with_regression

### 2023-08-02 H2.Rmd
re-ran some analyses for paper (almost ready to submit)

test1 <- subset(test, p < .05)
test1

@@

@@

>>>>

test1 <- subset(test, p < .05)
test1
test2 <- subset(test, p > .05)

@@

int_sig_pos <- pos_names # test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
int_sig_neg <- neg_names # test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
int_non_sig <- rownames(test2)

@@

symb_sig_pos <- pos_names # test1[which(test1$`mean F`>test1$`mean M`),] # subset(test1, d > 0)
symb_sig_neg <- neg_names # test1[which(test1$`mean F`<test1$`mean M`),] # subset(test1, d < 0)
symb_non_sig <- rownames(test2)
